News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-03-24 rupnik2015.tex
minor
likanje

\subsection{Problem definition}
\label{sec:tfidf}
\textbf{Document representation.}

Standard vector space model \cite{Salton88term-weightingapproaches} represents documents as vectors, where each term corresponds to word or phrase in a fixed vocabulary. More formally, document $d$ is represented by a vector $x \in \RR^n$, where $n$ corresponds to the size of the vocabulary, and vector elements $x_k$ correspond to the number of times term $k$ occurred in the document, also called \emph{term frequency} or $TF_k(d)$.

@@

\section{Cross-Lingual Models}\label{sec:models}
In this section, we describe several approaches to computing multilingual simliarities described in the previous section. We present three approaches
\begin{enumerate}
\item  a simple approach based on $k$-means clustering
\item  a standard approach based on singular value decomposition
\item a new method that is applicable in more general settings.
\end{enumerate}
 We concentrate on approaches that are based on linear maps rather than alternatives, such as machine translation and probabilistic models. Applicability of machine translation relies
on the availability of training resources (strongly aligned translation corpora), which are not available for many world languages, but there exist comparable corpora. Probabilistic
methods \todo{provide reasons for not using them: e.g. difficulty with parameter estimation, maybe just say future work?}.

For completeness we will also present the method of Canonical Correlation Analysis, since it is related to our proposed method.

@@

\subsection{Scaling}
\emph{I think that this section should be short.}
100 languages!
%Memory 100 GB per day
%Newsfeed volume 430k articles per day, 210k english, 36k Spanish, 27k German, 17k French, ....
%Number of similarities, 430k similarities every 200ms, currently could handle 1M articles,
%(n \over 2) 500X500 proxy matrices, 300000x500 Projector matrices, 430000x500 data
%Premultiply with proxy matrices, compare blockwise!
One of the main advantages of our approach is highly scalable. It is fast, very robust to quality of training data, easily extendable, simple to implement and has relatively small hardware requirements. The similarity pipeline is the most computationally intensive part and currently runs on two Intel Xeon E5-2667 v2, 3.30GHz processor machine with 256GB of RAM. This is sufficient to do similarity computation over 150 languages if needed. It currently uses Wikipedia as a freely available knowledge base and experiments show that the similarity pipeline dramatically reduces the search space when linking clusters.

@@

\acks{The authors wish to thank blah blah blah.}

>>>>

\subsection{Problem definition}\label{sec:tfidf}
We will start by describing how documents are represented as vectors and how to compare in a mono-lingual setting. We will then define a way to measure cross-lingual similarity that is natural for the models we consider.

\textbf{Document representation.} 
Standard vector space model \cite{Salton88term-weightingapproaches} represents documents as vectors, where each term corresponds to word or phrase in a fixed vocabulary. More formally, document $d$ is represented by a vector $x \in \RR^n$, where $n$ corresponds to the size of the vocabulary, and vector elements $x_k$ correspond to the number of times term $k$ occurred in the document, also called \emph{term frequency} or $TF_k(d)$.

@@

\section{Cross-Lingual Models}\label{sec:models}
In this section, we describe several approaches to computing multilingual simliarities described in the previous section. We present three approaches
\begin{enumerate}
\item  a simple approach based on $k$-means clustering
\item  a standard approach based on singular value decomposition
\item a new method that is applicable in more general settings.
\end{enumerate}
 We concentrate on approaches that are based on linear maps rather than alternatives, such as machine translation and probabilistic models, as discussed in the related work section. 
For completeness we will also present the method of Canonical Correlation Analysis, since it is related to our proposed method.

@@

\subsection{Scaling}
%\emph{I think that this section should be short.}
%100 languages!
%Memory 100 GB per day
%Newsfeed volume 430k articles per day, 210k english, 36k Spanish, 27k German, 17k French, ....
%Number of similarities, 430k similarities every 200ms, currently could handle 1M articles,
%(n \over 2) 500X500 proxy matrices, 300000x500 Projector matrices, 430000x500 data
%Premultiply with proxy matrices, compare blockwise!
One of the main advantages of our approach is highly scalable. It is fast, very robust to quality of training data, easily extendable, simple to implement and has relatively small hardware requirements. The similarity pipeline is the most computationally intensive part and currently runs on two Intel Xeon E5-2667 v2, 3.30GHz processor machine with 256GB of RAM. This is sufficient to do similarity computation over 150 languages if needed. It currently uses Wikipedia as a freely available knowledge base and experiments show that the similarity pipeline dramatically reduces the search space when linking clusters.

@@

%\acks{The authors wish to thank blah blah blah.}
